`flippant` --- An `R` package for the automated analysis of fluorescence--based

### 2016-12-15 inst/manuscript/manuscript.rmd
Add author emails as editorially requested;

>>>>

Author Emails
:   Richard J. Cotton: [richierocks@gmail.com](mailto:richierocks@gmail.com)\
    Birgit Ploier: [birgit.ploier@gmail.com](mailto:birgit.ploier@gmail.com)\
    Michael A. Goren: [wiscmag@gmail.com](mailto:wiscmag@gmail.com)\
    Anant K. Menon: [akm2003@med.cornell.edu](mailto:akm2003@med.cornell.edu)\
    Johannes Graumann: [jog2030@qatar-med.cornell.edu](mailto:jog2030@qatar-med.cornell.edu)
